MSSM-Penn-Pitt - ACC and DLPFC - FEATURECOUNTS - GRCh38 - CQN - Iterative Model

### 2020-05-01 code/CMC_ExpVal_DataProcessing.Rmd
Both Tissue Processing

  ggsave( filename=paste0( Tissue, "_Val.pdf" ),
    plot = ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
      geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
      theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)") ,
    device = "pdf",
    path = NULL,
    scale = 1,
    width = 14,
    height = 7,
    units = "in",
    dpi = 300,
    limitsize = TRUE
  )

>>>>

  ggsave( filename=paste0( Tissue, "_Val.pdf" ),
    plot = ggplot( data = Correlation, aes( x = Correlation, y = Log10_Pval, col = Sig ) ) + 
      geom_point() + ggtitle("Log10( PVal) vs. Correlation" ) + 
      theme(plot.title = element_text(hjust = 0.5)) + ylab("-Log( PValue)") ,
    device = "pdf",
    path = NULL,
    scale = 1,
    width = 21,
    height = 7,
    units = "in",
    dpi = 300,
    limitsize = TRUE
  )
